Predicting Spotify Audio Features from Last.fm Tags

### 2023-07-06 paper/main.tex
improvements

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.5\textwidth]{images/rmse_by_model_and_limit.png}
      \caption{RMSE mean and standard deviation by model and tags/tokens limit.}
      \label{fig:rmse_by_model_and_limit}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\textwidth]{images/rmse_by_model_and_feature.png}
      \caption{RMSE mean and standard deviation by model and audio feature.}
      \label{fig:rmse_by_model_and_feature}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\textwidth]{images/rmse_by_model_and_input.png}
      \caption{RMSE mean and standard deviation by model and input type (tag probablities or tokens).}
      \label{fig:rmse_by_model_and_input}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\textwidth]{images/rmse_by_feature_and_input.png}
      \caption{RMSE mean and standard deviation by audio feature and input type (tag probablities or tokens).}
      \label{fig:rmse_by_feature_and_input}
\end{figure}

>>>>

\begin{figure}[h!]
      \centering
      \includegraphics{images/rmse_by_model_and_limit.png}
      \caption{RMSE mean and standard deviation by model and tags/tokens limit.}
      \label{fig:rmse_by_model_and_limit}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics{images/rmse_by_model_and_feature.png}
      \caption{RMSE mean and standard deviation by model and audio feature.}
      \label{fig:rmse_by_model_and_feature}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics{images/rmse_by_model_and_input.png}
      \caption{RMSE mean and standard deviation by model and input type (tag probablities or tokens).}
      \label{fig:rmse_by_model_and_input}
\end{figure}

\begin{figure}[h!]
      \centering
      \includegraphics[width=1\textwidth]{images/rmse_by_feature_and_input.eps}
      \caption{RMSE mean and standard deviation by audio feature and input type (tag probablities or tokens).}
      \label{fig:rmse_by_feature_and_input}
\end{figure}
